Bird beak's elaboration and exploration

### 2022-10-17 Analysis/02-mcmcmcglmmm_analysis_variance_tests.Rmd
Update 02-mcmcmcglmmm_analysis_variance_tests.Rmd

```{r}
library(mcmcmcglmmm)
load(file = "../Data/Cluster/shapespace_allbirds_lvl_superorder_order/param_chains/params_shapespace_2D_9levels_20k.rda")
## Running the three MCMCglmm models
start <- Sys.time()
params_shapespace_2D_9levels_20k <- run.mini.chains(param_MCMCglmm, replicates = 1)
save(params_shapespace_2D_9levels_20k, file = "../Data/Processed/MCMCglmm/params_shapespace_2D_9levels_20k_chain1.rda")
end <- Sys.time()
end - start
```

```{r}
library(mcmcmcglmmm)
load(file = "../Data/Cluster/shapespace_allbirds_lvl_superorder_order/param_chains/params_shapespace_2D_9levels_20k.rda")
## Running the three MCMCglmm models
start <- Sys.time()
params_shapespace_2D_9levels_20k <- run.mini.chains(param_MCMCglmm, replicates = 1)
save(params_shapespace_2D_9levels_20k, file = "../Data/Processed/MCMCglmm/params_shapespace_2D_9levels_20k_chain2.rda")
end <- Sys.time()
end - start
```

```{r}
library(mcmcmcglmmm)
load(file = "../Data/Cluster/shapespace_allbirds_lvl_superorder_order/param_chains/params_shapespace_2D_9levels_20k.rda")
## Running the three MCMCglmm models
start <- Sys.time()
params_shapespace_2D_9levels_20k <- run.mini.chains(param_MCMCglmm, replicates = 1)
save(params_shapespace_2D_9levels_20k, file = "../Data/Processed/MCMCglmm/params_shapespace_2D_9levels_20k_chain3.rda")
end <- Sys.time()
end - start
```

@@

```{r}
library(mcmcmcglmmm)
load(file = "../Data/Cluster/shapespace_allbirds_lvl_superorder_order/param_chains/params_shapespace_8D_32levels_20k.rda")
## Running the three MCMCglmm models
start <- Sys.time()
params_shapespace_8D_32levels_20k <- run.mini.chains(param_MCMCglmm, replicates = 1)
save(params_shapespace_8D_32levels_20k, file = "../Data/Processed/MCMCglmm/params_shapespace_8D_32levels_20k_chain1.rda")
end <- Sys.time()
end - start
```

```{r}
library(mcmcmcglmmm)
load(file = "../Data/Cluster/shapespace_allbirds_lvl_superorder_order/param_chains/params_shapespace_8D_32levels_20k.rda")
## Running the three MCMCglmm models
start <- Sys.time()
params_shapespace_8D_32levels_20k <- run.mini.chains(param_MCMCglmm, replicates = 1)
save(params_shapespace_8D_32levels_20k, file = "../Data/Processed/MCMCglmm/params_shapespace_8D_32levels_20k_chain2.rda")
end <- Sys.time()
end - start
```

```{r}
library(mcmcmcglmmm)
load(file = "../Data/Cluster/shapespace_allbirds_lvl_superorder_order/param_chains/params_shapespace_8D_32levels_20k.rda")
## Running the three MCMCglmm models
start <- Sys.time()
params_shapespace_8D_32levels_20k <- run.mini.chains(param_MCMCglmm, replicates = 1)
save(params_shapespace_8D_32levels_20k, file = "../Data/Processed/MCMCglmm/params_shapespace_8D_32levels_20k_chain3.rda")
end <- Sys.time()
end - start
```

@@

```{r, get_model_parameters, eval = FALSE}
## Load the computed models
param_chains <- list()
for(i in 1:3) {
    load(paste0("../Data/Cluster/shapespace_allbirds_lvl_superorder_order/param_chains/shapespace_allbirds_lvl_superorder_order_param", i, ".rda"))
    param_chains[[i]] <- shapespace_allbirds_lvl_superorder_order_param[[1]]
}
## Extract the parameters from the parameter chains
est_params <- extract.parameters(param_chains)
```

@@

## Set up the mini-chains models
shapespace_allbirds_lvl_superorder_order_2D <- make.mini.chains(
                                data         = shapespace,
                                dimensions   = 1,
                                tree         = trees_list[sample(1:1000, 1000)],
                                trait.family = "gaussian",
                                randoms      = c("global", "level1"),
                                residuals    = "global",
                                priors       = est_params$priors,
                                verbose      = TRUE,
                                parameters   = list(
                                    nitt   = est_params$burnin + thin * samples,
                                    thin   = thin,
                                    burnin = est_params$burnin))
## Save the mini.chains
save(shapespace_allbirds_lvl_superorder_order_2D, file = "../Data/Cluster/shapespace_allbirds_lvl_superorder_order/shapespace_allbirds_lvl_superorder_order_2D.mini.chains")
```

@@

>>>>

```{r}
library(mcmcmcglmmm)
load(file = "../Data/Cluster/shapespace_allbirds_lvl_superorder_order/param_chains/params_shapespace_2D_9levels_20k.rda")
## Running the three MCMCglmm models
start <- Sys.time()
params_shapespace_2D_9levels_20k <- run.mini.chains(param_MCMCglmm, replicates = 1)
save(params_shapespace_2D_9levels_20k, file = "../Data/Cluster/shapespace_allbirds_lvl_superorder_order/param_chains/params_shapespace_2D_9levels_20k_chain1.rda")
end <- Sys.time()
end - start
```

```{r}
library(mcmcmcglmmm)
load(file = "../Data/Cluster/shapespace_allbirds_lvl_superorder_order/param_chains/params_shapespace_2D_9levels_20k.rda")
## Running the three MCMCglmm models
start <- Sys.time()
params_shapespace_2D_9levels_20k <- run.mini.chains(param_MCMCglmm, replicates = 1)
save(params_shapespace_2D_9levels_20k, file = "../Data/Cluster/shapespace_allbirds_lvl_superorder_order/param_chains/params_shapespace_2D_9levels_20k_chain2.rda")
end <- Sys.time()
end - start
```

```{r}
library(mcmcmcglmmm)
load(file = "../Data/Cluster/shapespace_allbirds_lvl_superorder_order/param_chains/params_shapespace_2D_9levels_20k.rda")
## Running the three MCMCglmm models
start <- Sys.time()
params_shapespace_2D_9levels_20k <- run.mini.chains(param_MCMCglmm, replicates = 1)
save(params_shapespace_2D_9levels_20k, file = "../Data/Cluster/shapespace_allbirds_lvl_superorder_order/param_chains/params_shapespace_2D_9levels_20k_chain3.rda")
end <- Sys.time()
end - start
```

@@

```{r}
library(mcmcmcglmmm)
load(file = "../Data/Cluster/shapespace_allbirds_lvl_superorder_order/param_chains/params_shapespace_8D_32levels_20k.rda")
## Running the three MCMCglmm models
start <- Sys.time()
params_shapespace_8D_32levels_20k <- run.mini.chains(param_MCMCglmm, replicates = 1)
save(params_shapespace_8D_32levels_20k, file = "../Data/Cluster/shapespace_allbirds_lvl_superorder_order/param_chains/params_shapespace_8D_32levels_20k_chain1.rda")
end <- Sys.time()
end - start
```

```{r}
library(mcmcmcglmmm)
load(file = "../Data/Cluster/shapespace_allbirds_lvl_superorder_order/param_chains/params_shapespace_8D_32levels_20k.rda")
## Running the three MCMCglmm models
start <- Sys.time()
params_shapespace_8D_32levels_20k <- run.mini.chains(param_MCMCglmm, replicates = 1)
save(params_shapespace_8D_32levels_20k, file = "../Data/Cluster/shapespace_allbirds_lvl_superorder_order/param_chains/params_shapespace_8D_32levels_20k_chain2.rda")
end <- Sys.time()
end - start
```

```{r}
library(mcmcmcglmmm)
load(file = "../Data/Cluster/shapespace_allbirds_lvl_superorder_order/param_chains/params_shapespace_8D_32levels_20k.rda")
## Running the three MCMCglmm models
start <- Sys.time()
params_shapespace_8D_32levels_20k <- run.mini.chains(param_MCMCglmm, replicates = 1)
save(params_shapespace_8D_32levels_20k, file = "../Data/Cluster/shapespace_allbirds_lvl_superorder_order/param_chains/params_shapespace_8D_32levels_20k_chain3.rda")
end <- Sys.time()
end - start
```

@@

```{r, get_model_parameters, eval = FALSE}
## Load the computed models
param_chains <- list()
for(i in 1:3) {
    load(paste0("../Data/Cluster/shapespace_allbirds_lvl_superorder_order/param_chains/params_shapespace_2D_9levels_20k_chain", i, ".rda"))
    param_chains[[i]] <- params_shapespace_2D_9levels_20k[[1]]
}
## Extract the parameters from the parameter chains
est_params <- extract.parameters(param_chains)
```

@@

## Set up the mini-chains models
shapespace_allbirds_lvl_superorder_order_2D <- make.mini.chains(
                                data         = shapespace,
                                dimensions   = 1:2,
                                tree         = trees_list[sample(1:1000, 1000)],
                                trait.family = "gaussian",
                                randoms      = c("global", "level1"),
                                residuals    = "global",
                                priors       = est_params$priors,
                                verbose      = TRUE,
                                parameters   = list(
                                    nitt   = est_params$burnin + thin * samples,
                                    thin   = thin,
                                    burnin = est_params$burnin))
## Save the mini.chains
save(shapespace_allbirds_lvl_superorder_order_2D, file = "../Data/Cluster/shapespace_allbirds_lvl_superorder_order/shapespace_allbirds_lvl_superorder_order_2D.mini.chains")
```

@@

```{r}
library(mcmcmcglmmm)
load(file = "../Data/Cluster/shapespace_allbirds_lvl_superorder_order/shapespace_allbirds_lvl_superorder_order_2D.mini.chains")
## Running the three MCMCglmm models
start <- Sys.time()
shapespace_allbirds_lvl_superorder_order_2D <- run.mini.chains(shapespace_allbirds_lvl_superorder_order_2D, replicates = 20)
save(shapespace_allbirds_lvl_superorder_order_2D, file = "../Data/Cluster/shapespace_allbirds_lvl_superorder_order/param_chains/params_shapespace_2D_9levels_20k_chain1_20.rda")
end <- Sys.time()
end - start
```
